The globular cluster system of the Auriga simulations

### 2020-04-09 AurigaGCS.tex
Specify the number of star particles in each of the subsets

Throughout our analysis we compare distributions of age-selected GC 
candidates (age $>10$~Gyr) with those of all star particles (i.e.
when no additional selection criterion is applied). We further split the GC
candidates into an {\it in~situ} subset (defined as GC candidates that are 
bound to the most-massive halo/subhalo in the first snapshot that the particle 
was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} and 
are bound to the most-massive halo/subhalo at $z=0$). A GC candidate either formed
{\it in~situ} or it was accreted. We consider the metallicity distribution in 
Sec.~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
Sec.~\ref{sec:results_Rgc}, and the combination of both 
in Sec.~\ref{sec:results_FeHRgc}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21-trim}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candidates in beige, and use a beige dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (brown), and those that have been accreted (teal).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

>>>>

Throughout our analysis we compare distributions of age-selected GC 
candidates (age $>10$~Gyr) with those of all star particles (i.e.
when no additional selection criterion is applied). The mean number of star 
particles in the Auriga L4 simulations that we select as GC candidates is 
$3.1 \cdot 10^5$ (with a mean mass of $1.15 \cdot 10^{10}$ M$_{\odot}$), 
and the mean number of all star particles is $1.93 \cdot 10^6$ 
($7.3\cdot10^{10}$ M$_{\odot}$). The subset of GC candidates is thus around 
15\% of all the stars in the galaxy. We further split the GC
candidates into an {\it in~situ} subset (defined as GC candidates that are 
bound to the most-massive halo/subhalo in the first snapshot that the particle 
was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} and 
are bound to the most-massive halo/subhalo at $z=0$). A GC candidate either formed
{\it in~situ} or it was accreted. We consider the metallicity distribution in 
Sec.~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
Sec.~\ref{sec:results_Rgc}, and the combination of both 
in Sec.~\ref{sec:results_FeHRgc}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21-trim}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candidates in beige, and use a beige dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (brown), and those that have been accreted (teal).
        The numbers in parenthesis show how many star particles are included 
        in the subset.
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. 
:/The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.
